Segmentation Using Attributes

### 2010-05-01 trunk/paper.tex
changes

%-------------------------------------------------------------------------------
% abstract
%-------------------------------------------------------------------------------
\begin{abstract}
Attributes have been shown to be effective in assisting object detection and
classification, and they provide means to also incorporate semantic
information available to and provided by humans.  On another front, the
combination of segmentation and object classification has been shown to
improve both segmentation and classification.  We present a method of incorporating
attributes into segmentation using a hierarchical methodology.
That is, using attributes as features, we discover attributes of regions
at all levels of a hierarchical segmentation, 
incorporate hierarchical confidences in determining a confidence that
a given region is part of a given object, and segment the image using
these confidences.  We also present results from experiments run using
this method.
\end{abstract}

@@

\begin{figure}
\label{fig:truck}
\centering
\subfigure[]{
\label{fig:trucka}
\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
}
\subfigure[]{
\label{fig:truckb}
\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
}
\caption{Segmentation by maximizing attribute saliency.  \subref{fig:trucka} shows
the original image with any ``car'' attributes that were predicted.  $P$ is the probability
that the image contains a car.  \subref{fig:truckb} shows the segmented image after
running our segmentation tree pruning algorithm.  As extraneous regions are pruned
more car attributes are predicted and the probability that the remaining image 
contains a car increases.}
\end{figure}

@@

This paper is organized as follows: we first discuss related work (\S \ref{sec:related_work})
and then present the algorithm in detail (\S \ref{sec:technical}).  We then discuss results from
a small-scale experiment on images from the pascal 2008 dataset (\S \ref{sec:results}), after which we draw
conclusions and discuss future directions (\S \ref{sec:conclusions}).

%-------------------------------------------------------------------------------
% related work
%-------------------------------------------------------------------------------
\section{Related work}
\label{sec:related_work}
A significant amount of recent work has been done in the area of using
attributes as high-level features for image classification and object
description \cite{farhadi09, lampert09, kumar09}.  
Another area of computer vision, that of segmentation,
has seen a resurgence of popularity as methods to incorporate top-down
information into segmentation have been shown to be highly effective
\cite{borenstein04, pantofaru, gu09, russell06, malisiewicz, leibe04, hoiem05, shotton06}.  
We propose to leverage research done in both of these areas -- attributes
and top-down/bottom-up segmentation -- to produce a combined approach.

@@

Attributes are high-level features which can reflect some semantic properties of objects. Given the attributes, we can do object detection based on the their distribution. We use the same attributes set as \cite{farhadi09}. This set contains three types of attributes, including Shape, Part and Material. All the attributes are listed in figure ?.

@@

\begin{figure*}
\label{fig:tree}
\centering
\subfigure[]{
\label{fig:treea}
\includegraphics[width=0.45\textwidth]{figures/tree_additive.eps}
}
\subfigure[]{
\label{fig:treeb}
\includegraphics[width=0.45\textwidth]{figures/tree_subtractive.eps}
}
\caption{The two segmentation hierarchies used by the additive \subref{fig:treea}
and subtractive \subref{fig:treeb} algorithms.  The additive hierarchy breaks the
regions into smaller and smaller regions, while the subtractive hierarchy increases
the size of the regions as smaller and smaller chunks are removed from the image.}
\end{figure*}

@@

This prune algorithm is based on three observations. (1) At least one node in the segmentation tree contrains the whole object. (This is always true since the root node contains the whole image). (2) If both parrent node and child node have high confidence as the object, the segment of child node is more accurate than that of the parrent node. (3) Even if the some node has high confidence as the object, its segmentation still need to improve. The details of the additive algorithm is shown in alg ?.\\

The idea of this algorithm is to find out the minimum discriminative segments, either positive or negative, and combine all of them together to form the final segment. We give three threshold for the similarity measure, $thre\_perf$, $thre\_pos$ and $thre\_neg$ which represent perfect segment, positive segment and negative segment, respectively. If the similarity is above $thre\_perf$, which means the segment is a perfect object, we cut all the nodes below and return this segment. If the similarity is below $thre\_neg$, which means the segment is impossible to be related to the object, we cut all the nodes below too and return NULL. If the similarity is between $thre\_perf$ and $thre\_pos$, which means the node definitely contains the object but the segmentation is not perfect yet, we keep on checking its children nodes to refine the segmentation. The final case is that the similarity is between $thre\_pos$ and $thre\_neg$, which means we are not sure whether there is an object in the node, so we just keep on searching its children. \\

The object detection is based on the output of ADDITIVE\_PRUNE. If the output is not NULL, which means at least one node in the tree has similarity above $thre\_pos$, we think the object is detected in this image.\\

(We also plan to do the vertical confidence propogation. But the experiment is too slow, we cannot incorporate it in this draft. We will show it in the final paper.)\\

\begin{algorithm}
\begin{algorithmic}
  \STATE \textbf{input:} 
  \STATE \hspace{3 mm} node $n$ in segmentation tree
  \STATE \hspace{3 mm} desired object model $obj\_model$
  \STATE \hspace{3 mm} threshold for perfect segment $thre\_perf$
  \STATE \hspace{3 mm} threshold for positive segment $thre\_pos$
  \STATE \hspace{3 mm} threshold for negative segment $thre\_neg$
  \STATE \textbf{output:} 
  \STATE \hspace{3 mm} refined segment 
  \STATE
  \STATE $sim=HI(obj\_model,n.conf)$
  \IF{$sim \ge thre\_perf$}
    \STATE return $n.segment$
  \ENDIF
  \IF{$sim \le thre\_neg$}
    \STATE return $NULL$
  \ENDIF
  \STATE $s'=NULL$
  \FOR{$i=1$ to $n.childNum$} 
    \STATE s\{i\}=ADDITIVE\_PRUNE(n.children\{i\},obj\_model,...
    \STATE ... thre\_perf,thre\_pos,thre\_neg)
    \STATE s'=s'+s\{i\}
  \ENDFOR
  \IF{$sim\ge thre\_pos$ and $s'==NULL$}
    \STATE return n.segment
  \ELSE
    \STATE return s'
  \ENDIF
\end{algorithmic}
\caption{ADDITIVE\_PRUNE}
\label{alg:add_prun}
\end{algorithm}

@@

The subtractive algorithm relies on the idea that if removing a region from
an image doesn't significantly affect the probability of the image containing
the object (which probability is obtained using the predicted attribute 
distribution) then that region can be safely removed in the final segmentation.
The algorithm itself is shown in algorithm \ref{alg:sub_prune}.

\begin{algorithm}
\begin{algorithmic}[1]
  \STATE \textbf{input:} 
  \STATE \hspace{3 mm} node $n$ in segmentation tree
  \STATE \hspace{3 mm} master mask $m_m$
  \STATE \hspace{3 mm} probability $P_{root}$ on root node
  \STATE \hspace{3 mm} factor $f$
  \STATE $m_n$ := mask of $n$
  \STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
  \STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
  \IF{$P_{pred} < f P_{root}$}
    \STATE SUBTRACTIVE\_PRUNE(n.children)
  \ELSE
    \STATE $m_m = m_m \cap m_n$
  \ENDIF
\end{algorithmic}
\caption{SUBTRACTIVE\_PRUNE}
\label{alg:sub_prun}
\end{algorithm}

The subtractive algorithm begins at the root of the tree and predicts attributes.
This attribute distribution and its associated probability $P_{root}$ is assumed to be
canonical for the image.  That is, any final segmentation should not have
significantly less probability $P_{pred}$ than $P_{root}$.  The algorithm traverses
the subtractive tree depth-first, predicting on each node.  
Any node that doesn't have a significant negative effect on the probability
of the presence of the object is removed.  This test is done on line 9.  If the
predicted probability was significantly affected, then we know that the region
must remain.  But it doesn't mean that sub-regions might be able to be pruned
out.  So the procedure is called recursively, checking for smaller regions
that might be able to be pruned (line 10).

If the probability was not significantly affected, then the mask is applied
(line 12) and no recursive call is made.  This is important, because it means
that we can remove large chunks of the image wholesale and bypass predicting
on the node's posterity.

$f$ is an important parameter that requires tuning.  Increasing $f$ makes the
algorithm more conservative, that is, less likely to apply removals.  Decreasing
$f$ makes it more liberal.  We found $f=0.9$ to be a reasonable value for most images.
Figure \ref{fig:f} shows results of adjusting $f$.

@@

\subsection{Dataset}
\label{ssec:dataset}

We use Pascal2008

Here are some results.
 trained using images from the pascal 
2008 dataset using the same annotations used in \cite{farhadi09}.

%-------------------------------------------------------------------------------
% conclusions and future work
%-------------------------------------------------------------------------------
\section{Conclusions and future work}
\label{sec:conclusions}
Highly dependent on attribute selection and discriminatory ability of attributes.

>>>>

%-------------------------------------------------------------------------------
% abstract
%-------------------------------------------------------------------------------
\begin{abstract}
Attributes have been shown to be effective in assisting object detection and
classification, and they provide means to also incorporate semantic
information available to and provided by humans.  On another front, the
combination of segmentation and object classification has been shown to
improve both segmentation and classification.  We present a method of incorporating
attributes into segmentation using a hierarchical methodology.
That is, using attributes as features, we discover attributes of regions
at all levels of a hierarchical segmentation, 
incorporate hierarchical confidences in determining a confidence that
a given region is part of a given object, and segment the image using
these confidences.  We also present encouraging segmentation results 
from experiments run using this method.
\end{abstract}

@@

\begin{figure}
\centering
\subfigure[]{
\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
\label{fig:trucka}
}
\subfigure[]{
\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
\label{fig:truckb}
}
\caption{Segmentation by maximizing attribute saliency.  \subref{fig:trucka} shows
the original image with any ``car'' attributes that were predicted.  $P$ is the probability
that the image contains a car.  \subref{fig:truckb} shows the segmented image after
running our segmentation tree pruning algorithm.  As extraneous regions are pruned
more car attributes are predicted and the probability that the remaining image 
contains a car increases.}
\label{fig:truck}
\end{figure}

@@

%This paper is organized as follows: we first discuss related work (\S \ref{sec:related_work})
%and then present the algorithm in detail (\S \ref{sec:technical}).  We then discuss results from
%a small-scale experiment on images from the pascal 2008 dataset (\S \ref{sec:results}), after which we draw
%conclusions and discuss future directions (\S \ref{sec:conclusions}).

%-------------------------------------------------------------------------------
% related work
%-------------------------------------------------------------------------------
\section{Related work}
\label{sec:related_work}
[Note: this section was lifted straight from our extended abstract
and has not yet been updated to reflect what we actually did.]

A significant amount of recent work has been done in the area of using
attributes as high-level features for image classification and object
description \cite{farhadi09, lampert09, kumar09}.  
Another area of computer vision, that of segmentation,
has seen a resurgence of popularity as methods to incorporate top-down
information into segmentation have been shown to be highly effective
\cite{borenstein04, pantofaru, gu09, russell06, malisiewicz, leibe04, hoiem05, shotton06}.  
We propose to leverage research done in both of these areas -- attributes
and top-down/bottom-up segmentation -- to produce a combined approach.

@@

Attributes are high-level features which can reflect semantic properties of objects. Given the attributes, we can do object detection based on the their distribution. We use the same attribute set as \cite{farhadi09}. This set contains three types of attributes, including shape, part and material. All attributes are listed in figure \ref{fig:atts}.

\begin{figure}
\begin{tabular}{llll}
2D Boxy & 3D Boxy & Round & Vert Cyl \\
Horiz Cyl & Occluded & Tail & Beak \\
Head & Ear & Snout & Nose \\
Mouth & Hair & Face & Eye \\
Torso & Hand & Arm & Leg \\
Foot/Shoe & Wing & Propeller & Jet engine \\
Window & Row Wind & Wheel & Door \\
Headlight & Taillight & Side mirror & Exhaust \\
Pedal & Handlebars & Engine & Sail \\
Mast & Text & Label & Furn. Leg \\
Furn. Back & Furn. Seat & Furn. Arm & Horn \\
Rein & Saddle & Leaf & Flower \\
Stem/Trunk & Pot & Screen & Skin \\
Metal & Plastic & Wood & Cloth \\
Furry & Glass & Feather & Wool \\
Clear & Shiny & Vegetation & Leather \\
\end{tabular}
\caption{List of attributes trained.}
\label{fig:atts}
\end{figure}

@@

\begin{figure*}
\centering
\subfigure[]{
\label{fig:treea}
\includegraphics[width=0.45\textwidth]{figures/tree_additive.eps}
}
\subfigure[]{
\label{fig:treeb}
\includegraphics[width=0.45\textwidth]{figures/tree_subtractive.eps}
}
\caption{The two segmentation hierarchies used by the additive \subref{fig:treea}
and subtractive \subref{fig:treeb} algorithms.  The additive hierarchy breaks the
regions into smaller and smaller regions, while the subtractive hierarchy increases
the size of the regions as smaller and smaller chunks are removed from the image.}
\label{fig:tree}
\end{figure*}

@@

This pruning algorithm is based on three observations. (1) At least one node in the segmentation tree contrains the whole object. (This is always true since the root node contains the whole image). (2) If both parent node and child node have high confidence of containing the object, the segmentation of the child node is more accurate than that of the parrent node. (3) Even if the same node has high confidence of containing the object, its segmentation can still improve. The details of the additive algorithm is shown in algorithm \ref{alg:add_prune}.

The idea of the algorithm is to find the smallest discriminative regions, either positive or negative, and combine all of them together to form the final segmentation. We use three threshold for the similarity measure, $thre\_perf$, $thre\_pos$ and $thre\_neg$ which represent perfect segment, positive segment and negative segment, respectively. If the similarity is above $thre\_perf$, which means the segmentation is perfect, we cut all the nodes below and return this segment. If the similarity is below $thre\_neg$, which means the segment does not contain the object, we cut all the nodes below and return NULL. If the similarity is between $thre\_perf$ and $thre\_pos$, which means the node definitely contains the object but the segmentation is not perfect yet, we keep on checking its children nodes to refine the segmentation. The final case is that the similarity is between $thre\_pos$ and $thre\_neg$, which means we are not sure whether there is an object in the node, so we just keep on searching its children.

The object detection is based on the output of ADDITIVE\_PRUNE. If the output is not NULL, which means at least one node in the tree has similarity above $thre\_pos$, we think the object is detected in this image.

(We also plan to do the vertical confidence propogation. But due to the slowness of the experiment, we cannot incorporate it in this draft. We will show it in the final paper.)

\begin{algorithm}
\begin{algorithmic}
  \STATE \textbf{input:} 
  \STATE \hspace{3 mm} node $n$ in segmentation tree
  \STATE \hspace{3 mm} desired object model $obj\_model$
  \STATE \hspace{3 mm} threshold for perfect segment $thre\_perf$
  \STATE \hspace{3 mm} threshold for positive segment $thre\_pos$
  \STATE \hspace{3 mm} threshold for negative segment $thre\_neg$
  \STATE \textbf{output:} 
  \STATE \hspace{3 mm} refined segment 
  \STATE
  \STATE $sim=HI(obj\_model,n.conf)$
  \IF{$sim \ge thre\_perf$}
    \STATE return $n.segment$
  \ENDIF
  \IF{$sim \le thre\_neg$}
    \STATE return $NULL$
  \ENDIF
  \STATE $s'=NULL$
  \FOR{$i=1$ to $n.childNum$} 
    \STATE s\{i\}=ADDITIVE\_PRUNE(n.children\{i\},obj\_model,...
    \STATE ... thre\_perf,thre\_pos,thre\_neg)
    \STATE s'=s'+s\{i\}
  \ENDFOR
  \IF{$sim\ge thre\_pos$ and $s'==NULL$}
    \STATE return n.segment
  \ELSE
    \STATE return s'
  \ENDIF
\end{algorithmic}
\caption{ADDITIVE\_PRUNE}
\label{alg:add_prune}
\end{algorithm}

@@

The subtractive algorithm relies on the idea that if removing a region from
an image doesn't significantly affect the probability of the image containing
the object (which probability is obtained using the predicted attribute 
distribution and is here used interchangably used with the term ``similarity'')
then that region can be safely removed in the final segmentation.
The algorithm itself is shown in algorithm \ref{alg:sub_prune}.

\begin{algorithm}
\begin{algorithmic}
  \STATE \textbf{input:} 
  \STATE \hspace{3 mm} node $n$ in segmentation tree
  \STATE \hspace{3 mm} master mask $m_m$
  \STATE \hspace{3 mm} similarity $sim_{root}$ on root node
  \STATE \hspace{3 mm} factor $f$
  \STATE $m_n$ := mask of $n$
  \STATE $pred\_model$ := predict attributes on image($m_n \cap m_m$)
  \STATE $sim=HI(obj\_model,pred\_model)$
  %\STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
  %\STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
  \IF{$sim < f sim_{root}$}
    \FOR{$i=1$ to $n.childNum$} 
      \STATE s\{i\}=SUBTRACTIVE\_PRUNE(n.children\{i\},$m_m$,
      \STATE ...$sim_{root}$, $f$)
    \ENDFOR
    %\STATE SUBTRACTIVE\_PRUNE(n.children)
  \ELSE
    \STATE $m_m = m_m \cap m_n$
  \ENDIF
\end{algorithmic}
\caption{SUBTRACTIVE\_PRUNE}
\label{alg:sub_prune}
\end{algorithm}

The algorithm begins at the root of the tree and predicts attributes.
This attribute distribution and its associated similarity $sim_{root}$ 
to the object's canonical distribution is taken to be
the standard for the image.  That is, any final segmentation should not have
significantly less similarity $sim$ than $sim_{root}$.  The algorithm traverses
the subtractive tree depth-first, predicting on each node.  
Any node that doesn't have a significant negative effect on the similarity as 
compared to the standard is removed.  If the
similarity was significantly affected, then we know that the region
must remain.  But it doesn't mean that sub-regions might not be able to be pruned
out, so the procedure is called recursively, checking for smaller regions
that might be able to be pruned.

If the probability was not significantly affected, then the mask is applied
and no recursive call is made.  This is important, because it means
that we can remove large chunks of the image wholesale and bypass predicting
on the node's posterity.

$f$ is an important parameter that requires tuning.  Increasing $f$ makes the
algorithm more conservative, that is, less likely to apply removals.  Decreasing
$f$ makes it more liberal.  We found $f=0.9$ to be a reasonable value for most images.
Figure \ref{fig:f} shows results of adjusting $f$ between 0.9 and 1.0.

@@

%\subsection{Dataset}
%\label{ssec:dataset}

We use the Pascal2008 dataset.  The attribute annotations used in \cite{farhadi09}
are freely available and we used them for training the attributes.

\ref{table:aresults} shows some of the results from running the additive algorithm
on all cars in the dataset.  The recall is the rate of correctly detecting
images with cars.  The segmentation precision is calculated with
\[ V(M_{model},M_{pred}) = \frac{|M_{model} \cap M_{pred}|}{|M_{model} \cup M_{pred}|} \]
where $M_{model}$ is the model mask calculated from the bounding boxes
stored with the annotations and $M_{pred}$ is the predicted segmentation
mask.  We of course recognize that the bounding boxes are not a good measure
of segmentation truth, but it's the best we have available.

The segmentation precision for the additive algorithm
is far better than the precision for the subtractive algorithm (which averaged
0.09).  This is because the additive algorithm only segments images for
which it has predicted presence of a car, so that any image pruned by the
algorithm already has a high car similarity score, enhancing the segmentation.
The subtractive algorithm, on the other hand, assumes presence of a car in
the image and proceeds no matter how poor the initial similarity score is.
(For the final paper we expect to have results comparing the precision
of the two algorithms based only on images segmented by both.)

Figures \ref{fig:good_results} and \ref{fig:bad_results} show the results
of segmentations of various images by both images.  This shows clear linkage
between prominence of the side profile of the car and success of the segmentation.
It appears that the attribute classifiers are more accurate on side profiles
than front and rear shots, although rear shots performed reasonably well when
tail lights were not illuminated.

\begin{table}
\centering
\begin{tabular}{|l|l|l|l|}
\hline
$P$ & $D$ & recall & prec \\ \hline
4, 1 & 227 & 0.4317 & 0.2393 \\ \hline
4, 1.5 & 239 & 0.3849 & 0.2370 \\ \hline
6, 1.5 & 239 & 0.2720 & 0.2501 \\ \hline
\end{tabular}
\caption{Results from the additive algorithm on all car images.  $P$ is
the parameters, $D$ is the number of detections, recall is the detection
recall rate and prec is the segmentation precision on all detected
images.}
\label{table:aresults}
\end{table}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/results/2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_000828.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_000952.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_002198.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/a2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_000828.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_000952.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_002198.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/b2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_000828.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_000952.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_002198.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008 
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/results/2008_002483.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_007466.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_005378.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_007529.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/a2008_002483.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_007466.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_005378.jpg.eps} &
Car not detected &
\includegraphics[width=3.95cm]{figures/results/a2008_007529.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/b2008_002483.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_007466.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_005378.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_007529.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008 
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:bad_results}
\end{figure*}

%-------------------------------------------------------------------------------
% conclusions and future work
%-------------------------------------------------------------------------------
\section{Discussion}
\label{sec:discussion}
It can be seen that in simple cases both additive and subtractive algorithms
are able to segment out rough outlines of the objects.  In most cases, even
the more difficult ones, at least part of the car was present in the final
segmentation.  This shows that the segmentation algorithms appear to be
reasonable approximations to a combinatoric approach -- that of predicting
on every combination of regions in the image.

Despite these encouraging initial results, the final segmentation region 
was often not coherent.
This appears to be largely because the region tree approach is not
constrained by spatial coherence.  That is, two leaf nodes containing image
regions that are spatially next to each other may be very distant in the
region tree.  Because of this, the attribute distribution may change significantly
after considering the first node and before consideration of the second node.
Another reason for this may be that our canonical attribute distribution for
our objects gave equal weights to each attribute.  For example, a wheel was
equally as important as shininess.  This gave unfair disadvantages to
under-represented or ill-trained attributes.  This can be seen in the results
where the body of the car is removed while the wheels or headlights are
retained.

As object detection is generally only as good as the features used, so also it
appears that this approach to segmentation is only as good as the attribute
selection and training.  We found that in images with poor segmentations, the
confidences in prediction of car attributes were generally low.  One problem
with this implementation of attribute classifiers was that we didn't use 
the selection criterion described in \cite{farhadi09} that enhances within
category prediction ability.  This means that, for example, the wheel attribute
is highly similar to the car attribute and thus its discrimative ability
is hurt.  One future direction for this research would be to improve the attribute
training using the additional selection criterion and observe effects on
the segmentations.

An interesting orthogonal direction that could be taken with these ideas is to
use segmentation using attributes as a diagnostic tool for attribute classifiers.
That is, the segmentations produced by our algorithms can help zero in on areas
in an image that exhibit high responses in detection of certain attributes.
For example, an image could be segmented using similarity to a canonical distribution
using only one attribute.  If that attribute is ``fur'' and segmentations
consistently show paws and tails, then it would quickly become clear that
the fur attribute classifier has learned on something other than fur.

The holy grail of this approach, of course, is to be able to segment objects
for which the canonical attribute distribution is unknown, based on a measure
of attribute coherence.  If this can be achieved, then segmentation experiments
could open up to non-experts, who could define coherence measures based on
semantic attributes and then could use this approach to automatically segment large
numbers of images even if no detection of their desired object exists.
